---
title: "AE 16: Civil liberties"
format: 
  html:
    toc: true
editor: visual
---

```{r}
#| label: load-packages-data
#| message: false

library(tidyverse)
library(gganimate)
```

```{r}
#| label: load-data
#| message: false

freedom <- read_csv("data/freedom.csv", na = "-")
```

## Task 1: Data wrangling

-   Find countries to plot -- those with highest standard deviation in civil liberties scores - and subset the data for these countries.

```{r}
#| label: freedom-to-plot

# add code here
```

-   Create a ranked dataset of these countries, and mark Turkey (or another country of interest).

```{r}
#| label: freedom-ranked

# add code here
```

## Task 2: Faceted plot

Create a faceted plot, with one facet for each year.

```{r}
#| label: freedom-faceted-plot
#| fig-width: 16
#| fig-asp: 1

# add code here
```

## Task 3: Animated plot

-   Create an animated plot object for the faceted plot with transitions between each year.

```{r}
#| label: freedom-bar-race

# add code here
```

-   Animate the plot.

```{r}
#| label: freedom-animate

# add code here
```
